---
title: "607 Projet1"
author: "Chunmei Zhu"
date: "September 21, 2017"

output:
  html_document:
  css: ./lab.css
highlight: pygments
theme: cerulean
pdf_document: default
---

#### Read in source file from my computer

```{r}
library(stringr)

raw.data <- readLines("D:/CUNY_SPS_DA/607_Data_Aq/Projet1/source_file/tournamentinfo.txt")
head(raw.data,10)

nrow <-length(raw.data)  #Number of the row in the file

```

#### Check data from the source file 

```{r}
raw.data[5]
raw.data[6]
```

## Get charactors from rows and check data in extraction 
```{r}
chars1 <- unlist(str_extract_all(raw.data[5], "[[:alnum:][:alnum:].*, ]{2,}"))
chars1
chars1[2] #get name
length(chars1)

chars2 <- unlist(str_extract_all(raw.data[6], "[[:alnum:][:alnum:].*, ]{2,}"))
chars2
chars2[1] #get location name
length(chars2)

```

## Create two tables to store data from the source file
### a vector "table1" for the row of player's id, name and record- a string as a list in factor type 
### a vector "df" for the row of player's location and  - a string as a list in factor type 


```{r}
j <- 0
k <- 0
table1=c()
df=c()

for(i in 5:nrow) {
    
    remainder1 <- (i-2)%%3
    remainder2 <- i%%3
    
    # Create table "table1":player's names
    if(remainder1 == 0) {
      j <-j+1
      table1[j] <-data.frame(unlist(str_extract_all(raw.data[i], "[[:alnum:][:alnum:].*\\-?*//[:alnum:], ]{2,}")))
    }
    
    # Create table "df":player's scores
    else if(remainder2 == 0) {
      k <- k+1
      df[k] <-data.frame(unlist(str_extract_all(raw.data[i], "[[:alnum:][:alnum:].*, ]{2,}")))
    }
    else{ i<-i+1 } 
}

print(j) # number of player
print(table1[j]) # last player info
print(table1[[j]][1]) # last player's ID
print(table1[[j]][2]) # last player's name

#print(df[[k]]) # last player info
print(df[[k]][1]) # last player's location
print(df[[k]][4]) # last player's pre_Rtg

```

##Contrust a data frame to store the data we need from two vectors
###create vectors for variables
###clearn data

```{r}
Id=c()
name=c()
location=c()
pre_Rtg=c()
total=c()
round1=c()
round2=c()
round3=c()
round4=c()
round5=c()
round6=c()
round7=c()

for(i in 1:j){
  
  #create vectors for variables
  Id[i] <- as.character(table1[[i]][1])
  name[i] <- as.character(table1[[i]][2])
  location[i] <- as.character(df[[i]][1])
  pre_Rtg[i] <- as.character(df[[i]][4])
  total[i]<- as.character(table1[[i]][3])
  round1[i]<- as.character(table1[[i]][4])
  round2[i]<- as.character(table1[[i]][5])
  round3[i]<- as.character(table1[[i]][6])
  round4[i]<- as.character(table1[[i]][7])
  round5[i]<- as.character(table1[[i]][8])
  round6[i]<- as.character(table1[[i]][9])
  round7[i]<- as.character(table1[[i]][10])
  
  
  #clear data
  Id[i] <-as.numeric(as.character(str_replace_all(Id[i], pattern = " ", replacement = "")))
  name[i] <-unlist(str_extract_all(name[i], "\\b[[:alpha:].*\\-?*\\>, ]{2,}"))
  location[i] <-str_replace_all(location[i], pattern = " ", replacement = "")
  pre_Rtg[i] <-as.numeric(as.character(unlist(str_extract_all(pre_Rtg[i],"[:digit:]+"))))
  total[i]<-as.numeric(as.character(str_replace_all(total[i], pattern = " ", replacement = "")))
  
  round1[i] <-str_sub(round1[i], start= -2)
  round1[i] <-as.numeric(as.character(str_replace_all(round1[i], pattern = " ", replacement = "")))
  round2[i] <-str_sub(round2[i], start= -2)
  round2[i] <-as.numeric(as.character(str_replace_all(round2[i], pattern = " ", replacement = "")))
  round3[i] <-str_sub(round3[i], start= -2)
  round3[i] <-as.numeric(as.character(str_replace_all(round3[i], pattern = " ", replacement = "")))
  round4[i] <-str_sub(round4[i], start= -2)
  round4[i] <-as.numeric(as.character(str_replace_all(round4[i], pattern = " ", replacement = "")))
  round5[i] <-str_sub(round5[i], start= -2)
  round5[i] <-as.numeric(as.character(str_replace_all(round5[i], pattern = " ", replacement = "")))
  round6[i] <-str_sub(round6[i], start= -2)
  round6[i] <-as.numeric(as.character(str_replace_all(round6[i], pattern = " ", replacement = "")))
  round7[i] <-str_sub(round7[i], start= -2)
  round7[i] <-as.numeric(as.character(str_replace_all(round7[i], pattern = " ", replacement = "")))
}

#Check data 
head(name,1)
head(location,1)
head(pre_Rtg,1)
head(total,1)
head(round1,1)
head(round2,1)
head(round3,1)
head(round4,1)
head(round5,1)
head(round6,1)
head(round7,1)

#Check special values
head(Id,5)
name[28]
pre_Rtg[8]
```

###combining vectors into a data frame


```{r}
mydata <- data.frame(Id,name,location,pre_Rtg,total,round1,round2,round3,round4,round5,round6,round7)
head(mydata,5)
dim(mydata)
str(mydata)

```

###Clear data type in mydata 

```{r}
  
  mydata$Id <- as.numeric(as.character(mydata$Id ))
  mydata$name <- as.character(mydata$name )
  mydata$location <- as.character(mydata$location)
  mydata$pre_Rtg <- as.numeric(as.character(mydata$pre_Rtg))
  mydata$total<- as.numeric(as.character(mydata$total))
  mydata$round1<- as.numeric(as.character(mydata$round1))
  mydata$round2<- as.numeric(as.character(mydata$round2))
  mydata$round3<- as.numeric(as.character(mydata$round3))
  mydata$round4<- as.numeric(as.character(mydata$round4))
  mydata$round5<- as.numeric(as.character(mydata$round5))
  mydata$round6<- as.numeric(as.character(mydata$round6))
  mydata$round7<- as.numeric(as.character(mydata$round7))
  
  str(mydata)
  summary(mydata)
  

```

## Replace values in each round by their pre_Rtg values

```{r}
for (i in 1:j){
   r1 <- mydata$round1[i]
   r2 <- mydata$round2[i]
   r3 <- mydata$round3[i]
   r4 <- mydata$round4[i]
   r5 <- mydata$round5[i]
   r6 <- mydata$round6[i]
   r7 <- mydata$round7[i]

  mydata$round1[i] <- mydata$pre_Rtg[r1] 
  mydata$round2[i] <- mydata$pre_Rtg[r2]
   mydata$round3[i] <- mydata$pre_Rtg[r3] 
  mydata$round4[i] <- mydata$pre_Rtg[r4]
   mydata$round5[i] <- mydata$pre_Rtg[r5] 
  mydata$round6[i] <- mydata$pre_Rtg[r6]
   mydata$round7[i] <- mydata$pre_Rtg[r7] 
  
}
head(mydata)
dim(mydata)

```

## Calculation of Average of scores of rounds
###insert new column avg in mydata 
###get sum of scores in each row and calculate the avg of each


```{r}
mydata["avg"] <- 0

mydata[mydata=="" ]<-0

for(i in 1:j){ 
 colSums(mydata[,c(6,12)], na.rm = TRUE)

mydata$avg[i] <-as.integer((mydata$round1[i]+mydata$round2[i]+mydata$round3[i]+mydata$round4[i]+mydata$round5[i]+ mydata$round6[i]+ mydata$round7[i])/7)

}

head(mydata$avg)
head(mydata)

```

##Required outcome 
  
```{r}
#outcome_string <- data.frame(mydata$name,mydata$location, mydata$total,mydata$pre_Rtg,mydata$avg)
#summary(outcome)
#head(outcome)

outcome_string<- data.frame(paste(mydata$name,mydata$location, mydata$total,mydata$pre_Rtg,mydata$avg, sep = ","))
head(outcome_string)

write.table(outcome_string, "D:/CUNY_SPS_DA/607_Data_Aq/Projet1/mydata.txt", sep="\t")

```

Note 
